Plots and tables summarizing results of Poisson simulations

### 2018-12-21 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

This script produces supplementary tables for Poisson simulations.

*Explain which set of results correspond to the plots given in the main
text.*

>>>>

Here we create plots and tables to compare SMASH and against other
methods for reconstructing a spatially structured signal from
Poisson-distributed data. Similar to the Gaussian simulations, we
generated data sets using a variety of test functions and intensity
ranges. Specifically, we considered 6 test functions, rescaling the
test function so that the smallest intensity was x and the largest
intensity was y, with (x,y) set to either (1/100, 3), (1/8, 8) or
(1/128, 128). For each combination of test function and intensity
range, we simulated 100 data sets. In the plots and tables below, We
summarize the error (MISE) in the estimates from the 100 data sets in
each setting.

The plots below summarizing the results from the "Bursts" simulations
were included in the manuscript.
